---
title: "Data"
format:
  html:
    code-overflow: wrap
---

You can access a `.csv` with detailed RPV estimates and their confidence intervals, for every state.

## Election data sources

2016 and 2020 estimates use [Voting and Election Science Team](https://dataverse.harvard.edu/dataverse/electionscience) precinct returns aligned by the ALARM Project's [2020 Redistricting Data Files](https://alarm-redist.github.io/posts/2021-08-10-census-2020/).

2024 estimates use precinct-level returns compiled for [Kenny (2026)](https://osf.io/preprints/socarxiv/svktd_v1). [Redistricting Data Hub](https://redistrictingdatahub.org/) provided returns for AL, AZ, GA, IL, KS, LA, MA, MD, MO, MS, NC, NE, NH, OH, SC, TN, TX, UT, VA, WA, and WI. New York returns come from [Benjamin J. Rosenblatt](https://www.benjrosenblatt.com/2024general-live-results) and Twitter's `@cincy9`. California and Michigan data were collected directly from state and local election offices by Christopher T. Kenny. Returns for the remaining states were collected by [Josh Metcalf](https://github.com/21MetcalfJ/2024Precincts).

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(htmltools)
HTML(readLines("state-svg-defs.svg"))

```

```{r}
#| echo: false

raw <- gh::gh('GET /repos/electionlawclinic/rpvnearme/contents/data/')
files <- keep(raw, ~ str_ends(.$name, pattern = 'summary\\.csv')) %>%
  map_dfr(~ tibble(
    abb = str_to_upper(str_sub(.$name, 1, 2)),
    type = if_else(.$name %in% c('CA', 'HI', 'OR'), 'Census tracts', 'VTDs'),
    filename = .$name,
    url = .$download_url
  ))
files <- files %>%
  left_join(select(censable::stata, abb, state = name), by = 'abb') %>%
  arrange(state)
pmap(files, function(state, abb, type, filename, url, ...) {
  a(
    href = url, target = '_blank', download = filename,
    div(
      tags$svg(
        class = paste0('icon icon-state-', abb),
        style = 'height: 1.8em; width: 2.0em; position: relative; top: 0em;',
        tags$use(`xlink:href` = paste0('#icon-state-', abb))
      ),
      HTML('&nbsp;'),
      strong(state, ' ', type),
      HTML('&nbsp;'),
      fontawesome::fa('circle-down'),
      HTML('&nbsp;'),
      code(filename, style = 'color: #777777;'),
      tags$br()
    )
  )
}) %>%
  as.tags()

```

<br>

## Using the data

### Data Format

In the current iteration, data summaries are available for contested statewide and federal elections within each county in the United States. Almost all counties are included, except for a small number of extremely small counties with too few precincts or voting districts to produce estimates.

In the summary files, each observation is identified by `county`, `race`, and `cand`.

-   `county`: County name
-   `race`: voter race
    -   `white`: White
    -   `black`: Black
    -   `hisp`: Hispanic
    -   `oth`: Other race or ethnicity (not White, Black, or Hispanic)
-   `cand`: candidate
-   `mean`: mean estimate of support
-   `sd`: standard deviation of the estimate
-   `ci_95_lower`: lower bound for the 95% confidence interval
-   `ci_95_upper`: upper bound for the 95% confidence interval
