---
title: "Data"
format:
  html:
    code-overflow: wrap
---

You can access a `.csv` with detailed RPV estimates and their confidence intervals, for every state.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(htmltools)
HTML(readLines("state-svg-defs.svg"))

```

```{r echo = FALSE}
raw <- gh::gh('GET /repos/electionlawclinic/rpvnearme/contents/data/')
files <- keep(raw, ~ str_ends(.$name, pattern = 'summary\\.csv')) %>%
  map_dfr(~ tibble(
    abb = str_to_upper(str_sub(.$name, 1, 2)),
    type = if_else(.$name %in% c('CA', 'HI', 'OR'), 'Census tracts', 'VTDs'),
    filename = .$name,
    url = .$download_url
  ))
files <- files %>%
  left_join(select(censable::stata, abb, state = name), by = 'abb') %>%
  arrange(state)
pmap(files, function(state, abb, type, filename, url, ...) {
  a(
    href = url, target = '_blank', download = filename,
    div(
      tags$svg(
        class = paste0('icon icon-state-', abb),
        style = 'height: 1.8em; width: 2.0em; position: relative; top: 0em;',
        tags$use(`xlink:href` = paste0('#icon-state-', abb))
      ),
      HTML('&nbsp;'),
      strong(state, ' ', type),
      HTML('&nbsp;'),
      fontawesome::fa('circle-down'),
      HTML('&nbsp;'),
      code(filename, style = 'color: #777777;'),
      tags$br()
    )
  )
}) %>%
  as.tags()

```

<br>

## Using the data

### Data Format

In the current iteration, data summaries are available for contested statewide and federal elections within each county in the United States. Almost all counties are included, except for a small number of extremely small counties with too few precincts or voting districts to produce estimates.

In the summary files, each observation is identified by `county`, `race`, and `cand`.

-   `county`: County name
-   `race`: voter race
    -   `white`: White
    -   `black`: Black
    -   `hisp`: Hispanic
    -   `oth`: Other race or ethnicity (not White, Black, or Hispanic)
-   `cand`: candidate
-   `mean`: mean estimate of support
-   `sd`: standard deviation of the estimate
-   `ci_95_lower`: lower bound for the 95% confidence interval
-   `ci_95_upper`: upper bound for the 95% confidence interval
